The data samples used in this thesis come from $pp$ collision data collected with the ATLAS detector from 2022 through 2024 during Run-3 at the LHC\@. This data was collected with $\com{} = 13.6$ TeV with bunch spacing of 25 ns and a total integrated luminosity of 165.4 fb$^{-1}$~\cite{atlas_lumi_image} collected with a 2\% uncertainty.

All events used in this thesis are required to pass some lepton trigger selection. To pass the L1 trigger, muons are required to have $\pt > 14$ GeV for all three data taking years. Electrons have varying L1 requirements by data taking year. For 2022, electrons must have $\pt > 22$ GeV and satisfy a very tight isolation requirement, whereas in 2023 and 2024, the threshold increased to $\pt > 26$ GeV with the same isolation requirement.

At the HLT muons can pass the trigger in one of two ways: either by having $\pt > 24$ GeV and passing a medium identification working point, or by having $\pt > 50$ GeV without any additional identification requirement. Electrons HLT requirements are consistent across all three years and have three ways to pass the trigger: First, electron $\pt > 26$ GeV with tight identification and loose isolation, secondly electron $\pt > 60$ GeV and medium identification, and finally electron $\pt > 140$ GeV with a loose identification.

Events are included in the thesis only if they were collected during periods marked as good runs in the GRL and if at least one lepton satisfies the single-lepton trigger selection. A summary of the GRLs can be seen in Table~\ref{tab:grl}, and lepton triggers in Table~\ref{tab:triggers}.

\begin{table}
  \centering
  \begin{tabularx}{1.12\textwidth}{c|>{\centering\arraybackslash}X}
    \hline
    \textbf{Data year} & \textbf{Good Runs List} \\
    \hline
    2022 & data22\_13p6TeV.periodAllYear\_DetStatus-v134-pro28-10\_MERGED\_PHYS\_StandardGRL\_All\_Good\_25ns\_ignore\_TRIGLAR.xml \\ 
    \hline
    2023 & data23\_13p6TeV.periodAllYear\_DetStatus-v133-pro31-11\_MERGED\_PHYS\_StandardGRL\_All\_Good\_25ns\_ignoreTRIG\_JETCTPIN.xml \\
    \hline
    2024 & physics\_25ns\_data24.xml \\
    \hline
  \end{tabularx}
  \caption{Summary of the Good Runs Lists (GRL) used in this thesis. The GRL defines the periods of data taking that are suitable for physics analysis.}\label{tab:grl}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{c|c|c}
    \hline
    \textbf{Data Year} & \textbf{Muon Trigger} & \textbf{Electron Trigger} \\
    \hline
    2022 & \makecell[l]{HLT\_mu24\_ivarmedium\_L1MU14FCH \\ HLT\_mu50\_L1MU14FCH} & \makecell[l]{HLT\_e26\_lhtight\_ivarloose\_L1EM22VHI \\ HLT\_e60\_lhmedium\_L1EM22VHI \\ HLT\_e140\_lhloose\_L1EM22VHI} \\
    \hline
    2023 & \makecell[l]{HLT\_mu24\_ivarmedium\_L1MU14FCH \\ HLT\_mu50\_L1MU14FCH} & \makecell[l]{HLT\_e26\_lhtight\_ivarloose\_L1eEM26M \\ HLT\_e60\_lhmedium\_L1eEM26M \\ HLT\_e140\_lhloose\_L1eEM26M} \\
    \hline
    2024 & \makecell[l]{HLT\_mu24\_ivarmedium\_L1MU14FCH \\ HLT\_mu50\_L1MU14FCH} & \makecell[l]{HLT\_e26\_lhtight\_ivarloose\_L1eEM26M \\ HLT\_e60\_lhmedium\_L1eEM26M \\ HLT\_e140\_lhloose\_L1eEM26M} \\
    \hline
  \end{tabular}
  \caption{Summary of the lepton triggers used in this thesis. The muon trigger requires either a medium identification working point or a high $\pt$ threshold, while the electron trigger has three different thresholds and identification requirements.}\label{tab:triggers}
\end{table}

